### 2014-10-25 Docs/getting_started/getting_started.tex
update docs

>>>>

\item {\tt flame} \\[-3mm]

   A combustion-mode problem where we model a thermonuclear flame in a
   small domain.  This enforces the low Mach combustion constraint
   div{U} = S.  Hot ash and cool fuel are put into contact and a flame
   will ignite and propagate across the grid.  Inflow boundary
   conditions are used to allow for an inflow velocity to be set to
   keep the laminar flame stationary.

   In this mode, \maestro\ behaves like the code described
   in \cite{SNe}, which was used for models of Rayleigh-Taylor
   unstable flames~\cite{SNld,SNrt,SNrt3d}.
